---
title: "AS2-2: 股市動態"
author: "第 0 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: ../style.css
---

<hr>
基本的程式筆記設定，安裝、載入一些基本的套件
```{r results='hide', message=FALSE, warning=FALSE}
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8); options(scipen=20, digits=4, width=90)
if(!require(pacman)) install.packages("pacman")
pacman::p_load(magrittr)
```
以上這些程式碼請大家不要去改動<br>

- - -

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>
```{r}
IBM = read.csv('data/IBMStock.csv')
GE = read.csv('data/GEStock.csv')
PRO = read.csv('data/ProcterGambleStock.csv')
COCA = read.csv('data/CocaCOlaStock.csv')
BOE = read.csv('data/BoeingStock.csv')
```


###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
#
nrow(BOE)
nrow(COCA)
nrow(GE)
nrow(IBM)
nrow(PRO)
#
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
BOE$Date = as.Date(BOE$Date, format = '%m/%d/%y')
COCA$Date = as.Date(COCA$Date, format = '%m/%d/%y')
GE$Date = as.Date(GE$Date, format = '%m/%d/%y')
IBM$Date = as.Date(IBM$Date, format = '%m/%d/%y')
PRO$Date = as.Date(PRO$Date, format = '%m/%d/%y')

min(BOE$Date, na.rm = T)
min(COCA$Date, na.rm = T)
min(GE$Date, na.rm = T)
min(IBM$Date, na.rm = T)
min(PRO$Date, na.rm = T)

```

__§ 1.3__ What is the latest year in our datasets?
```{r}
#
max(BOE$Date, na.rm = T)

#
```
<br>

<span style="font-size:20px">`r "\U1F4A1"`</span>
資料框的序列 a list of data.frame
```{r}
#
#
```

```{r}
#
#
```

```{r}
#
#
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
#
mean(IBM$StockPrice)
#
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
#
min(GE$StockPrice)
#
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
#
max(COCA$StockPrice)
#
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
#
median(BOE$StockPrice)
#
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
#
sd(PRO$StockPrice)
#
```

<span style="font-size:20px">`r "\U1F4A1"`</span>
內建的統計量功能：`mean()`, `median()`, `sd()`, `min()`, `max()`, `range()`, `summary()`

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
#
COCA$Date[which.max(COCA$StockPrice)]
COCA$Date[which.min(COCA$StockPrice)]
#
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(subset(IBM, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', ylim = c(10,200))
lines(subset(COCA, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='red')
lines(subset(BOE, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='green')
lines(subset(PRO, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='blue')
lines(subset(GE, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='pink')
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
#
plot(subset(COCA, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(40,100),col = 'red')
lines(subset(PRO, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l' )
#
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#
plot(subset(COCA, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(10,200),col = 'red')
lines(subset(PRO, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(10,200), )
lines(subset(GE, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(10,200), col = 'green')
lines(subset(IBM, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(10,200), col = 'blue')
lines(subset(BOE, Date >'1983-01-01' & Date < '1983-12-31'), type = 'l', ylim = c(10,200), col = 'pink')
#BOE的股價較低
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
#
plot(subset(IBM, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', ylim = c(10,200))
lines(subset(COCA, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='red')
lines(subset(BOE, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='green')
lines(subset(PRO, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='blue')
lines(subset(GE, Date >'2000-01-01' & Date < '2000-12-31'), type = 'l', col='pink')
#GE的股票跌最多
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
plot(subset(IBM, Date >'1995-01-01' & Date < '2005-12-31'), type = 'l', ylim = c(10,200))
lines(subset(COCA, Date >'1995-01-01' & Date < '2005-12-31'), type = 'l', col='red')
lines(subset(BOE, Date >'1995-01-01' & Date < '2005-12-31'), type = 'l', col='green')
lines(subset(PRO, Date >'1995-01-01' & Date < '2005-12-31'), type = 'l', col='blue')
lines(subset(GE, Date >'1995-01-01' & Date < '2005-12-31'), type = 'l', col='pink')
#IBM的股票
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
#
subset(IBM, Date >'1997-09-01' & Date < '1997-11-30')
subset(COCA, Date >'1997-09-01' & Date < '1997-11-30')
subset(BOE, Date >'1997-09-01' & Date < '1997-11-30')
subset(PRO, Date >'1997-09-01' & Date < '1997-11-30')
subset(GE, Date >'1997-09-01' & Date < '1997-11-30')
#BOE,COCA 下跌
```

```{r}
#

#
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
#
plot(subset(IBM, Date >'2004-01-01' & Date < '2005-12-31'), type = 'l', ylim = c(10,200))
lines(subset(COCA, Date >'2004-01-01' & Date < '2005-12-31'), type = 'l', col='red')
lines(subset(BOE, Date >'2004-01-01' & Date < '2005-12-31'), type = 'l', col='green')
lines(subset(PRO, Date >'2004-01-01' & Date < '2005-12-31'), type = 'l', col='blue')
lines(subset(GE, Date >'2004-01-01' & Date < '2005-12-31'), type = 'l', col='pink')
#BOE 的股價表現最好
```

<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
#
which(tapply(BOE$StockPrice, format(BOE$Date, '%m'), mean) > mean(BOE$StockPrice))
#1~7月
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
#
which.max(tapply(COCA$StockPrice, format(BOE$Date, '%m'), mean) %>% round(digits = 2))
which.max(tapply(GE$StockPrice, format(BOE$Date, '%m'), mean) %>% round(digits = 2))
#
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
#
plot(tapply(BOE$StockPrice, format(BOE$Date, '%m'), mean), type = 'l', ylim = c(40,85))
lines(tapply(GE$StockPrice, format(GE$Date, '%m'), mean), type = 'l', col = 'green')
lines(tapply(COCA$StockPrice, format(COCA$Date, '%m'), mean), type = 'l', col = 'red')
lines(tapply(IBM$StockPrice, format(IBM$Date, '%m'), mean), type = 'l', col = 'blue')
lines(tapply(PRO$StockPrice, format(PRO$Date, '%m'), mean), type = 'l', col = 'orange')
#3~5, 10~12
```
<br>
<p class="wwl">
<span style="font-size:20px">`r "\U1F4DD"` UNIT2B 學習重點：</span><br>
The Magic of the `apply()` Series：<br>
&emsp; ■ `tapply(x, factor, fun)` : apply function to x by factor<br>
&emsp; ■ `lapply(list, fun)` : apply function to each element of a list<br>
&emsp; ■ `sapply()` : apply function to each element of a list and simplify the ouput<br>
</p class="wwl">
<br><br><br>

